Survey paper tables and figures

### 2021-10-01 survey/code/paper-tables.Rmd
Figure tweaks suggested by Josh

signals <- append(signals, list(anosmia)) %>%
  aggregate_signals(format = "long")

signals$signal <- factor(
  signals$signal,
  levels = c("anosmia", "raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
             "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  labels = c("Anosmia %", "CLI %", "Community CLI %", "Cases per 100,000",
             "Hospitalizations per 100,000", "Deaths per 100,000"))

@@

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "Value", color = "Census Region") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month",
               guide = guide_axis(angle = 45)) +
  theme_bw() +
  theme(legend.position = "bottom")

@@

@@

ggplot(symptom_rates, aes(x = symptom, y = rate, fill = positive_14d)) +
  geom_col(position = position_dodge()) +
  geom_pointrange(
    aes(x = symptom, y = rr / rr_scale_factor,
        ymin = rr_lower / rr_scale_factor,
        ymax = rr_upper / rr_scale_factor),
    data = symptom_rrs,
    inherit.aes = FALSE) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                     sec.axis = sec_axis(~ . * rr_scale_factor,
                                         name = "Relative risk")) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "", y = "Frequency among respondents",
       fill = "Group") +
  theme_bw() +
  theme(legend.position = "bottom")

@@

start_day <- floor_date(as.Date(min(data$StartDatetime)), unit = "week")
state_case_rate <- covidcast_signal("jhu-csse", "confirmed_7dav_cumulative_num",
                                    start_day = start_day,
                                    end_day = as.Date(max(data$StartDatetime)),
                                    geo_type = "state") %>%
  mutate(geo_value = toupper(geo_value),
         year = year(time_value),
         month = month(time_value)) %>%
  select(state = geo_value, cumulative_cases = value, time_value, year, month) %>%
  inner_join(state_pops, by = "state") %>%
  inner_join(case_age_dist, by = c("year", "month")) %>%
  mutate(case_rate_adult = cumulative_cases * frac_adult_cases / adult_pop * 100)

state_case_compare <- data %>%
  filter(!is.na(fips)) %>%
  mutate(
    ever_pos = case_when(
      B10a == "1" ~ TRUE,
      B11 == "1" ~ TRUE,
      B11 == "2" ~ FALSE,
      B8 == "2" ~ FALSE,
      TRUE ~ NA
    ),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    state_abbr = name_to_abbr(state_fips_to_name(fips))
  ) %>%
  group_by(week, state_abbr) %>%
  summarize(ever_pos = 100 * weighted.mean(ever_pos, weight, na.rm = TRUE),
            .groups = "drop") %>%
  left_join(state_case_rate,
            by = c("state_abbr" = "state", "week" = "time_value"))

g <- ggplot(state_case_compare) +
  facet_geo(~ state_abbr, grid = "us_state_with_DC_PR_grid1", label = "code") +
  geom_line(aes(x = week, y = case_rate_adult, color = "Surveillance"),
            linetype = 1, size = 0.5) +
  geom_line(aes(x = week, y = ever_pos, color = "CTIS"),
            linetype = 1, size = 0.5) +
  scale_color_manual(values = c("lightblue", "gray50")) +
  scale_y_continuous(breaks = c(0, 10),
                     minor_breaks = c(5, 15),
                     labels = label_percent(scale = 1,
                                            accuracy = 1)) +
  scale_x_date(date_breaks = "4 months", date_labels = "%b",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")

@@

a <- ggplot(g1, aes(x = week, y = value, col = SVI_cat, group = SVI_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "SVI") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0,  NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

b <- ggplot(g2, aes(x = week, y = value, col = age_cat, group = age_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Age") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

c <- ggplot(g3, aes(x = week, y = value, col = region, group = region)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Region")  +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  ylim(0, NA) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2))

@@

ggsave("../paper/fig/contacts-masks-transport.pdf", g, width = 8, height = 5)
```

>>>>

signals <- append(signals, list(anosmia)) %>%
  aggregate_signals(format = "long") %>%
  filter(!(signal == "confirmed_admissions_covid_1d_prop" &
             time_value < as.Date("2020-07-15")))

signals$signal <- factor(
  signals$signal,
  levels = c("anosmia", "raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
             "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  labels = c("Anosmia (%)", "CLI (%)", "Community CLI (%)", "Cases per 100,000",
             "Hospitalizations per 100,000", "Deaths per 100,000"))

@@

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "", color = "Census Region") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month",
               guide = guide_axis(angle = 45)) +
  scale_y_continuous(minor_breaks = NULL) +
  theme_bw() +
  theme(legend.position = "bottom",
        strip.background = element_rect(color = "black", fill = "white"))

@@

# Force factor ordering
data$positive_14d <- factor(
  data$positive_14d,
  levels = c("Tested positive", "All others"))

@@

ggplot(symptom_rates, aes(x = symptom, y = rate, fill = positive_14d)) +
  geom_col(position = position_dodge()) +
  geom_pointrange(
    aes(x = symptom, y = rr / rr_scale_factor,
        ymin = rr_lower / rr_scale_factor,
        ymax = rr_upper / rr_scale_factor),
    data = symptom_rrs,
    inherit.aes = FALSE) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                     sec.axis = sec_axis(~ . * rr_scale_factor,
                                         name = "Relative risk"),
                     minor_breaks = NULL) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "", y = "Frequency among respondents",
       fill = "Group") +
  theme_bw() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())

@@

start_day <- floor_date(as.Date(min(data$StartDatetime)), unit = "week")
state_case_rate <- covidcast_signal("jhu-csse", "confirmed_7dav_cumulative_num",
                                    start_day = start_day,
                                    end_day = as.Date(max(data$StartDatetime)),
                                    geo_type = "state") %>%
  mutate(geo_value = toupper(geo_value),
         year = year(time_value),
         month = month(time_value)) %>%
  select(state = geo_value, cumulative_cases = value, time_value, year, month) %>%
  inner_join(state_pops, by = "state") %>%
  inner_join(case_age_dist, by = c("year", "month")) %>%
  mutate(case_rate_adult = cumulative_cases * frac_adult_cases / adult_pop * 100) %>%
  filter(state != "PR")

state_case_compare <- data %>%
  filter(!is.na(fips)) %>%
  mutate(
    ever_pos = case_when(
      B10a == "1" ~ TRUE,
      B11 == "1" ~ TRUE,
      B11 == "2" ~ FALSE,
      B8 == "2" ~ FALSE,
      TRUE ~ NA
    ),
    week = floor_date(as.Date(StartDatetime), unit = "week"),
    state_abbr = name_to_abbr(state_fips_to_name(fips))
  ) %>%
  group_by(week, state_abbr) %>%
  summarize(ever_pos = 100 * weighted.mean(ever_pos, weight, na.rm = TRUE),
            .groups = "drop") %>%
  left_join(state_case_rate,
            by = c("state_abbr" = "state", "week" = "time_value"))
```

```{r case-rate-compare-plot}
g <- ggplot(state_case_compare) +
  facet_geo(~ state_abbr, grid = "us_state_grid1", label = "code") +
  geom_line(aes(x = week, y = case_rate_adult, color = "Surveillance"),
            linetype = 1, size = 0.5) +
  geom_line(aes(x = week, y = ever_pos, color = "CTIS"),
            linetype = 1, size = 0.5) +
  scale_color_manual(values = c("lightblue", "gray50")) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0, 10, 20),
                     minor_breaks = c(5, 15),
                     labels = label_percent(scale = 1,
                                            accuracy = 1)) +
  scale_x_date(breaks = as.Date(c("2020-10-01", "2021-04-01")),
               date_labels = "%b", minor_breaks = NULL) +
  labs(x = "", y = "", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text = element_text(size = rel(0.5)))

@@

a <- ggplot(g1, aes(x = week, y = value, col = SVI_cat, group = SVI_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "SVI") +
  scale_y_continuous(minor_breaks = NULL, limits = c(0, NA)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2),
        strip.background = element_rect(color = "black", fill = "white"))

b <- ggplot(g2, aes(x = week, y = value, col = age_cat, group = age_cat)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Age") +
  scale_y_continuous(minor_breaks = NULL, limits = c(0, NA)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2),
        strip.background = element_rect(color = "black", fill = "white"))

c <- ggplot(g3, aes(x = week, y = value, col = region, group = region)) +
  geom_line() +
  facet_wrap(. ~ var_cat, scales = "free", ncol = 4) +
  scale_color_discrete(name = "Region")  +
  scale_y_continuous(minor_breaks = NULL, limits = c(0, NA)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  labs(x = "", y = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.margin = margin(legend_top_margin, 0, 11 / 2, 0),
        plot.margin = margin(11 / 2, 11 / 2, 0, 11 / 2),
        strip.background = element_rect(color = "black", fill = "white"))

@@

ggsave("../paper/fig/contacts-masks-transport.pdf", g, width = 7, height = 6)
```
